Nengo: A Python tool for building large-scale functional brain models

### 2013-09-26 nengo.tex
Figures mostly done

%% This should be a paper of its own.

%% \subsection{Semantic Pointer Architecture (SPA)}

%% TODO; should we even include this section?
%% It could probably be a separate paper on its own.

@@

\begin{figure}
\begin{center}
  Nengo high-level object hierarchy
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:01} Figure \arabic{figure}.}{
   Nengo high-level object hierarchy}
\end{figure}

@@

\begin{figure}
\begin{center}
  Network code listing
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:01} Figure \arabic{figure}.}{
   Network code listing}
\end{figure}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=.9\textwidth]{comm_channel}
  \begin{minipage}{0.58\textwidth}
    \begin{lstlisting}
      import nengo
      from nengo.helpers import white_noise
      model = nengo.Model("Communication Channel")
      model.make_node("Input", white_noise(1, 5))
      model.make_ensemble("A", nengo.LIF(30), 1)
      model.make_ensemble("B", nengo.LIF(30), 1)
      model.connect("Input", "A")
      model.connect("A", "B")
      model.probe("Input")
      model.probe("A", filter=0.01)
      model.probe("A.spikes")
      model.probe("B", filter=0.01)
      model.probe("B.spikes")
      sim = model.simulator()
      sim.run(1)
      A_data = sim.data("A")
      A_spikes = sim.data("A.spikes")
      ...
    \end{lstlisting}
  \end{minipage}
  \begin{minipage}{0.37\textwidth}
    \includegraphics[width=\textwidth]{comm_channel_res}
  \end{minipage}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:cchannel} Figure \arabic{figure}.}{
   Communcation channel model. (Top) Cartoon depiction of the model.
   (Bottom left) Python code to create and run the model.
   (Bottom right) Results of the model simulation. Lines depict
   the node's output (Input panel) and the decoded value being represented
   by ensembles (A and B panels). Light gray lines in A and B panels denote
   spikes emitted by neurons in the ensembles. Each row depicts spikes
   for one neuron.}
\end{figure}

@@

      model.connect('State', 'State',
                      function=feedback, filter=tau)
      model.probe('State', filter=tau)
      model.probe('State.spikes')
      sim = model.simulator()
      sim.run(6)
    \end{lstlisting}
  \end{minipage}
  \begin{minipage}{0.55\textwidth}
    \includegraphics[width=0.95\textwidth]{lorenz}
    \includegraphics[width=\textwidth]{lorenz_res}
  \end{minipage}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:lorenz} Figure \arabic{figure}.}{
   Lorenz attractor model. (Left) Python code to create and run the model.
   (Top right) Cartoon depiction of the model.
   (Bottom right) Results of the model simulation. Lines depict
   the node's output (Input panel) and the decoded value being represented
   by ensembles (A and B panels). Light gray lines in A and B panels denote
   spikes emitted by neurons in the ensembles. Each row depicts spikes
   for one neuron.}
\end{figure}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.8\textwidth]{cconv}
  \begin{minipage}{0.53\textwidth}
    \begin{lstlisting}[basicstyle={\footnotesize\ttfamily}]
      import nengo
      from nengo.networks import CircularConvolution
      model = nengo.Model("Circular convolution")
      model.make_node("Input A", [-0.21, 0.5, 0.12, 0.06])
      model.make_ensemble("A", nengo.LIF(512), 4)
      model.connect("Input A", "A")
      model.make_node("Input B", [-0.18, 0.28, 0.18, -0.52])
      model.make_ensemble("B", nengo.LIF(512), 4)
      model.connect("Input B", "B")
      cconv = model.add(CircularConvolution("Circular Convolution",
          neurons=nengo.LIF(1032), dimensions=4))
      model.connect("A", cconv.A)
      model.connect("B", cconv.B)
      model.make_ensemble("Result", nengo.LIF(512), 4)
      model.connect(cconv, "Result")
      model.probe("A", filter=0.02)
      model.probe("B", filter=0.02)
      model.probe("Result", filter=0.02)
      sim = model.simulator()
      sim.run(0.5)
    \end{lstlisting}
  \end{minipage}
  \begin{minipage}{0.43\textwidth}
    \includegraphics[width=\textwidth]{cconv_res}
  \end{minipage}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:lorenz} Figure \arabic{figure}.}{
   Circular convolution model. (Top) Cartoon depiction of the model.
   Note that much of the complexity is contained within the
   circular convolution network; the transform matrices shown
   are automatically generated by the network depending on
   input dimensionality.
   (Bottom left) Python code to create and run the model.

@@

\begin{figure}
\begin{center}
  CConv benchmarks
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:01} Figure \arabic{figure}.}{
   CConv benchmarks}
\end{figure}

>>>>

\begin{figure}
\begin{center}
  \includegraphics[width=0.19\textwidth]{nef_summary_enc}
  \includegraphics[width=0.19\textwidth]{nef_summary_dec}
  \includegraphics[width=0.399\textwidth]{nef_summary_trans}
  \includegraphics[width=0.199\textwidth]{nef_summary_dyn}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:nef} Figure \arabic{figure}.}{
   Summary of the Neural Engineering Framework.}
\end{figure}

@@

@@

@@

\begin{figure}
\begin{center}
  \includegraphics[width=.9\textwidth]{comm_channel}
  \begin{minipage}{0.58\textwidth}
    \begin{lstlisting}
      import nengo
      from nengo.helpers import white_noise
      model = nengo.Model("Communication Channel")
      model.make_node("Input", white_noise(1, 5))
      model.make_ensemble("A", nengo.LIF(30), 1)
      model.make_ensemble("B", nengo.LIF(30), 1)
      model.connect("Input", "A")
      model.connect("A", "B")
      model.probe("Input")
      model.probe("A", filter=0.01)
      model.probe("A.spikes")
      model.probe("B", filter=0.01)
      model.probe("B.spikes")
      sim = model.simulator()
      sim.run(1)
      A_data = sim.data("A")
      A_spikes = sim.data("A.spikes")
      ...
    \end{lstlisting}
  \end{minipage}
  \begin{minipage}{0.37\textwidth}
    \includegraphics[width=\textwidth]{comm_channel_res}
  \end{minipage}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:cchannel} Figure \arabic{figure}.}{
   Communcation channel model. (Top) Diagram of the model.
   (Bottom left) Python code to create and run the model.
   (Bottom right) Results of the model simulation. Lines depict
   the node's output (Input panel) and the decoded value being represented
   by ensembles (A and B panels). Light gray lines in A and B panels denote
   spikes emitted by neurons in the ensembles. Each row depicts spikes
   for one neuron.}
\end{figure}

@@

      model.connect('State', 'State',
                      function=feedback, filter=tau)
      model.probe('State', filter=tau)
      model.probe('State.spikes')
      sim = model.simulator()
      sim.run(6)
    \end{lstlisting}
  \end{minipage}
  \begin{minipage}{0.55\textwidth}
    \includegraphics[width=0.95\textwidth]{lorenz}
    \includegraphics[width=\textwidth]{lorenz_res}
  \end{minipage}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:lorenz} Figure \arabic{figure}.}{
   Lorenz attractor model. (Left) Python code to create and run the model.
   (Top right) Diagram of the model.
   (Bottom right) Results of the model simulation. Lines depict
   the node's output (Input panel) and the decoded value being represented
   by ensembles (A and B panels). Light gray lines in A and B panels denote
   spikes emitted by neurons in the ensembles. Each row depicts spikes
   for one neuron.}
\end{figure}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.8\textwidth]{cconv}
  \begin{minipage}{0.53\textwidth}
    \begin{lstlisting}[basicstyle={\footnotesize\ttfamily}]
      import nengo
      from nengo.networks import CircularConvolution
      model = nengo.Model("Circular convolution")
      model.make_node("Input A", [-0.21, 0.5, 0.12, 0.06])
      model.make_ensemble("A", nengo.LIF(512), 4)
      model.connect("Input A", "A")
      model.make_node("Input B", [-0.18, 0.28, 0.18, -0.52])
      model.make_ensemble("B", nengo.LIF(512), 4)
      model.connect("Input B", "B")
      cconv = model.add(CircularConvolution("Circular Convolution",
          neurons=nengo.LIF(1032), dimensions=4))
      model.connect("A", cconv.A)
      model.connect("B", cconv.B)
      model.make_ensemble("Result", nengo.LIF(512), 4)
      model.connect(cconv, "Result")
      model.probe("A", filter=0.02)
      model.probe("B", filter=0.02)
      model.probe("Result", filter=0.02)
      sim = model.simulator()
      sim.run(0.5)
    \end{lstlisting}
  \end{minipage}
  \begin{minipage}{0.43\textwidth}
    \includegraphics[width=\textwidth]{cconv_res}
  \end{minipage}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:lorenz} Figure \arabic{figure}.}{
   Circular convolution model. (Top) Diagram of the model.
   Note that much of the complexity is contained within the
   circular convolution network; the transform matrices shown
   are automatically generated by the network depending on
   input dimensionality.
   (Bottom left) Python code to create and run the model.

@@

\section{Benchmarks}

Some stuff about benchmarking

\begin{figure}
\begin{center}
  \includegraphics[width=0.5\textwidth]{benchmark}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:benchmarks} Figure \arabic{figure}.}{
   Benchmarks}
\end{figure}
